Type Evolution in Interactive Programming Systems

### 2024-05-31 paper.tex
Add diagram with very sketchy description

>>>>

\frameworkbox{
\begin{wrapfigure}{r}{14.5em}
\vspace{-0.5em}
\includegraphics[width=14.5em]{figures/arr-model.png}
\vspace{-1.5em}
\end{wrapfigure}
\frameworkboxtitle{TODO}
Here, data $D_0$ now represent the state machine definition.
Live data that we obtain by instantiating the state machine still contain this state machine
definition, but also the necessary live state defined by the definition.

This is used to synthesize live machine state $+D_0$ conforming to live machine type $+T_0$.
This then runs producing $+T'_0$ and so on...

If the state machine definition changes from $D_0$ to $D_1$,
we can synthesize new live machine state $+D_1$ conforming to new live machine type $+T_1$.

The challenge is to merge these changes with the currently running state machine $+T'_0$.
We have to produce merged live machine type $+T_0 \diamond +T_1$ and also merge the
live state changes to obtain $+D'_0 \diamond +D_1$ of the new merged live machine type.
}
